TacticToe: Learning the Game of Tactics

### 2018-01-26 tactictoe_jv.tex
More

During our experiments,
We chose to distinguish two these general purpose tactic \metis and \eprover.
\metis is integrated in \holfour, so can be call with frequently with low 
timeout.
And the strongest external provers according to past experiments \cite{hh4h4}.
Where as...
external calls to \eprover are computationally expensive (5 seconds at a 
minimum +  128 premises), we  
experiment with a small hammer tactic comprised of: a faster premise 
selection algorithm and
a short call (0.1 seconds + 16 premises optimized by the previous paper) to the 
internal prover \metis~\cite{metis} or a
longer call to external prover \eprover.

@@

This is a generalization of the simplest method used for minimizing a list of 
theorems in ``hammers'' \cite{}. The fact that lists are generally small
make this approach feasible.

@@

>>>>

During our experiments,
We chose to distinguish two these general purpose tactic \metis and \eprover.
\metis is integrated in \holfour, so can be call with frequently with low 
timeout.
And the strongest external provers according to past experiments \cite{tgck-cpp15}.
Where as...
external calls to \eprover are computationally expensive (5 seconds at a 
minimum +  128 premises), we  
experiment with a small hammer tactic comprised of: a faster premise 
selection algorithm and
a short call (0.1 seconds + 16 premises optimized by the previous paper) to the 
internal prover \metis~\cite{metis} or a
longer call to external prover \eprover.

@@

This is a generalization of the simplest method used for minimizing a list of 
theorems in ``hammers'' \cite{hammers4qed}. The fact that lists are generally small
make this approach feasible.

@@

Proof patching: \cite{RingerYLG18}
